\section{Experience}
\resumeSubHeadingListStart
\resumeExpSubheading
{The Layer}{Remote}
{Machine Learning Engineer}{February 2024 - September 2024}
{AI Data Enrichment Platform}
\resumeDesc{
	\begin{itemize}
		\item Created multi-step LLM data ingestion pipelines, reducing the manual labor for client onboarding and data processing up to 90\%
		\item Shipped multimodal feature enrichment pipelines, reducing labeling costs up to 8$\times$ and attribute coverage by around 70\%.
		\item Scaled Airflow DAGs to process 10M+ items per minute, adding alerts, retries, data-quality checks, and business guardrails.
		      
	\end{itemize}
}\vspace{-7pt}

\resumeExpSubheading
{Sber}{Moscow, Russia}
{Data Scientist}{March 2023 - June 2023}
{Leading retail and corporate bank}
\resumeDesc{
	\begin{itemize}
		\item Built a data collection pipeline using PySpark to gather over 50M+ records on client defaults, enabling comprehensive modeling and analysis of default behavior over time.
		\item Proposed a credit scoring model based on survival curves and embeddings from XGBoost trees, achieving an average C-Index of 0.85 over a 3-5 year horizon.
	\end{itemize}}\vspace{-7pt}
\resumeExpSubheading
{Group-IB}{Moscow, Russia}
{Software Developer}{July 2022 - November 2022}
{A leading provider of cybersecurity solutions}
\resumeDesc{
	\begin{itemize}
		\item Integrated Cobalt Strike to Caldera framework, automating complex adversary emulation scenarios and enhancing the system's capability for advanced security testing with a 30\% increase in test coverage.
		\item Developed a benchmarking framework to optimize threat detection efficiency in the company's M-XDR solution, reducing product update release time by 40-60\%.
		\item Set up a robust CI/CD pipeline for seamless deployment of the framework to a multi-agent ESXi sandbox environment, speeding up the deployment process.
	\end{itemize}}\vspace{-7pt}
\resumeExpSubheading
{Zabra}{Saransk, Russia}
{Machine Learning Software Engineer}
{Mar 2020 - May 2022}
{Computer Vision Startup}
\resumeDesc{
	\begin{itemize}
		\item Designed and productionized a suite of auxiliary action detection models on top of tracking pipelines: entry/exit, item taking, etc., based on YOLOv4 architecture
		\item Drove model upgrades via 10+ paper reviews, improving robustness for multi-object tracking and detection.
		\item Shipped PPE-compliance analytics for Russian Railways by fusing CV detections with radio-transceiver IDs to associate workers and gear.
		\item Developed utilities for 3D scene data preparation and manipulation, accelerating data collection and model development
		\item Implemented and maintained REST APIs on GCP, powering the mobile app and store logic; built dashboards for key operational metrics.
	\end{itemize}
}
\resumeSubHeadingListEnd
